\subsection{Financial Stability of CBDC}

The literature on the financial disintermediation cause by CBDC is growling rapidly.
\citet*{FVSSU21} use a \citet*{DD83} framework to show that central bank has the
monopolistic power in the deposit market that can endanger the maturity
transformation for commercial banks.
\citet*{Keister19} uses a new monetary search model to prove that while CBDC
increases the efficiency in exchange, it inevitably crowd out bank deposits, and
cause the funding cost of a commercial bank to increase.

\begin{center}
(To be continued)
\end{center}

\subsection{CBDC in an Open Economy}
CBDC in an open economy is gaining large attention recently. \citet*{FMS22}
proves that the international spillover effect might be amplified using a
two-country DSGE model.

\begin{center}
(To be continued)
\end{center}

The closest model that addresses the issue of bank runs under cross-border CBDC
design is written by \citet{Popescu22}. Following \citet*{DD83}, the paper tries
to show that there are multiple equilibria of domestic bank is exposed in the
risk of a run. The model, however, only sees CBDC as a safe deposit, which is an
asset with interest rate, being a liability of the central bank. In reality,
agents might not want to deposit money in CBDC accounts solely due to it being
riskless, as it might not be the mean of payment widely used. This motivates the
methodology of using agent-based modelling, since it is capable of observing the
endogenous formation of CBDC as a means of payment, while simultaneously
activates an episode of fear through sentimental spreading.

\subsection{Agent-based Modeling}

\begin{center}
    Agent-based modeling intro
\end{center}

To motivate endogenous adoption of a certain means of payment, it is necessary
to embed a trading system. Several literatures propose the designs of this
system. The Complex Adaptive Trivial System (CATS) mentioned in
\citet*{HandbookABM}, agents (households) choose firms from the lowest price in
the market during a consumption bundle decision stage; also in
\citet*{HandbookABM} the two framework EUBI and EBGE chooses the goods to buy
according to a logistic probability depending on the price firms offer. As for
the decision process of the selection of which means of payment to use during a
trade, these macroeconomic agent-based models do not implement this as they
focus more on quantitatively matching the stylized fact of a business cycle.
\citet*{Sargent90-MoneyAI} studies a \citet*{KW98} economy using a classifier
system evolving genetically to study the emergence of a medium of exchange.
\citet*{Manolis21} transforms an ABM model for language spreading into a study
for parallel circulation of currencies under a scale-free social
network.\footnote{In \citet*{Manolis21}, he generates a trading network using
preferential attachment, and according to network literatures, this network has
the property known as ``scale-free'' \citep*{Price1976}. As you shall see in my
model, I also follow this idea to create a synthetic scale-free bipartite
network as my international trading net.}
His model, however, does not study the formation during trading process, but through
simply a spreading process.
A more structural model that studies the selection of a payment system during a
repetitive trading process is \citet*{Trade_ABM_MOP2006}. They study how agents
adopt new payments systems using ABM, and the probability of selecting a
means of payment depends on the utility function of selecting it.

Although the literature of ABM is abundant regarding the trading process, there
is a crucial component that is missing, which unfortunately is the key to my
research --- the expectation for events. For macroeconomic agent-based models,
the expectation can be addressed by artificial neural networks (ANN) or genetic
algorithms (GA).  In the case of ANN, for each agent, several indicators and
errors between past expectation and realization are passed in as parameters, go
through several additional hidden layers, to receive the expectation for the
next period \citep*[see][]{Salle15-ABM_EXP}.  The GA approach considers a series of evolutionary
procedure such as selection, crossover, and mutation\citep*[see][]{Arifovic18-GA_EXP}.

In this paper, the expectation comes in three ways: expectation of future benefit
for holding a certain portfolio, expectation of a bank run episode, and the
expectation of the CBDC to be riskless. The second and third is a rare event, so
the above learning procedure is not suitable for the two expectation.
Bank run, however, can be triggered by simply implementing an imitation rule in
an ABM setting~\citep*{Santos2021}