\subsection{Basis Flow and Structure}

The model is composed of two open economies and three sectors --- buyers/sellers,
banks and governments. Each country issues its own currency, but all buyers have
the freedom to decide what means of payment (hereafter MoP) to use.  There is
an alternation of roles between buyers and sellers, with each transitioning to
the other role once a successful trade is conducted. This setting is to assure
that agents have the incentives to adjust its portfolio of MoP, conceptually
similar to the idea given in \citet*{TW95}. For each period, buyers decide how
much to consume and save, and base on the consumption budget, buyers meet with
sellers during a search and matching process.

MoP is then decided under each trade. Both buyers and sellers observe the
popularity of each Mop, hence deciding the optimal portfolio of MoP to hold.
%%%%%%%%%%%%%%%
\footnote{Under rational expectations, a representative agent looks forward and
chooses the optimal mean of payment that provides one the largest lifetime
utility. In the absence of perfect coordination and perfect foresight, however,
an agent might possibly hold a depreciating currency solely due to the fact that
it is the only means of payment widely used regionally.}
%%%%%%%%%%%%%%%
For every trade and portfolio reallocation that involves altering the banks'
ledger, the bank immediately records it. This in turn causes the leverage of the
bank to alter. The leverage of the bank is globally visible to all agents,
signalling the soundness of the financial environment. Sensitive agents are then
urged to withdraw any premature assets from the bank (in this model I consider
only the deposit) if they sense a signal of instability, and through a herding
behavior that bank is thus exposed to a risk of run. This herding behavior can be
modeled through introducing an imitation rule \citep*{Santos2021}. For
simplicity, the bank has an exogenous credit level. Doing so allows the result
to be focused on the effect of cross-border CBDC, instead of other financial
acceleration coming from the capital market \citep{BGG96}.

Central banks interest rates are temporarily set exogenously.
%% currently unclear whether the simple setting could cause inflation, and thus the Taylor rule is not compatible.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%
%%
%%
%Consumption Budget Decision
%%
%%
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Consumption Decision}

Following \citet*{HandbookABM}, consumption decision for a buyer is separated
into two steps: consumption budget and consumption bundle.

\subsubsection*{Consumption Budget}

We follow the simple keynesian setting and let the consumption be a proportion
of its disposable income

\begin{definition}[General Rule of Consumption]
   {\phantom{text} \\}
   For each buyer $b$ at time $t$, one consumes
   \begin{equation}
      C_{b,t} = \mathrm{MPC}\times \mathrm{DI}_{b,t} + a + \epsilon_t ,
   \end{equation}
   where $\mathrm{MPC}$ is the marginal propensity to consume, $\mathrm{DI}$ is
   the disposable income, $a$ is the minimal amount of expenditure, and
   $\epsilon$ is a random shock on consumption.
\end{definition}

\subsubsection*{Consumption Bundle}
After all buyers complete deciding its consumption budget, they proceed to decide the consumption bundle.

\begin{definition}
[Consumption Bundle Step]
\phantom{} \\
\begin{enumerate}
   \item Buyer $b$ selects candidate sellers $\{s \in \mathcal{N}_b\}$ from its
   trading network $\mathcal{N}_b$.\footnote{See Appendix \ref{sec-network} for detail on the
   network.}
   \item If seller $s$ is out of stock, proceed to the next candidate.
   \item If buyer $b$ itself is out of budget, one stops the consumption and the
   next buyer consumes.\footnote{In this agent-based model, buyers are activated
   randomly, but in order. In computer science this is called ``synchronous''.}
   \item During each trade, the agents go through a payment decision process.
\end{enumerate}
\end{definition}

The payment decision process (hereafter PDP) depends on the frequency of past
appearance, its opportunity cost of using it as a MoP (interest rate), its cost
of holding the asset (risk of confiscation or inflation rate), following the
functionalism view of money. Holding a MoP has different incentives from a
payment aspect and an asset aspect. The next part describes the procedure of a PDP\@.

\subsection{Payment Decision}

\newcommand{\MOP}{\mathrm{MOP}}
\newcommand{\mop}{\mathrm{mop}}

\subsubsection*{Notations}

At every moment (a tick in the simulation), an agent recognizes a set of MoP,
denoted as $\MOP_{a,t} = \{ \mop_1, \mop_2, \dots, \mop_{n(a,t)} \}$, where
$\mop$ denotes one kind of MoP, such as foreign country bank deposit or foreign
CBDC\@; $n(a,t)$ denotes the total number of means of payment that an agent sees
up to time $t$. If an agent discovers a new type of MoP, $n(a,t)$ increases by $1$.

Every agent has a record of the occurrence of each MoP it saw previously, denoted as
\begin{equation}
   F_{a,t} = \{f^m_t \mid m \in \MOP_{a,t}\} ,
\end{equation}

where $f^m_t$ represents the memorized occurrence of MoP $m$ at time $t$, accumulated according to an AR(1) process:
\begin{equation}
   f^m_{t+1} = \rho f^m_t + \Delta^m_t .
\end{equation}
The damping factor $\rho$ captures the ``memory'' of an agent, and $\Delta^m_t$
is the amount of MoP $m$ an agent has seen during all the transaction one done
during time $t$.
Also define the frequency of observation

\begin{equation}
   \tilde{F}_{a,t} = \left\{ \tilde{f}^m_t = \frac{f^m_t}{n_f} \mid  m \in \MOP_{a,t}\right\},
\end{equation}
where $n_f$ is the normalization factor, defined as the sum of all $f^m_t$
\begin{eqnarray*}
   n_{f} = \sum_{m \in \MOP_{a,t}} f^m_t \quad \forall a ,
\end{eqnarray*}

\begin{definition}
   [Acceptance of MoP]
   \phantom{}\\
   An agent accepts or pays with a MoP if and only if the frequency of
   observation exceeds some threshold. Denote the set of acceptance as
   \begin{equation}
      A_{a,t} = \left\{ m \in \MOP_{a,t} \mid \tilde{f}^m_{at}>threshold_a\right\}
   \end{equation}
\end{definition}

\subsubsection*{Random Utility Model}

An agent makes decision according to a probability vector. An agent has, for
each MoP, a collection of information regarding the specific MoP, and calculates
the utility for using it \citep*{Csik96,Matsatsinis00,Trade_ABM_MOP2006}

Assume that an agent's utility function for using a MoP $m$ is
\begin{equation}
   \label{eq:MOP-utility}
   V^m_{at} = U^m_{at}(\tilde{f}^m_{at}, i^m_t, X_t) + \varepsilon^m_{at} ,
\end{equation}
where $U(\cdot)$ is a deterministic utility function depending on the past
frequency of observing this MoP $\tilde{f}^m_{a,t}$, the interest rate $i^m_t$,
and other factors that an agent might take into consideration when choosing.

The error term $\varepsilon^m_{at}$ captures the idiosyncratic shock that an
agent faces when choosing. If we assume
that the error term follows a T1EV distribution
\begin{equation*}
   F(\varepsilon) = e^{-e^{-\varepsilon}}
\end{equation*}
the probability function will be in a logistic form \citep*{McFadden74}

\begin{definition}
   [Probability of MoP Selection]
   \begin{equation}
      P(m \mid \tilde{f}^m_{at}, i^m_t, X_t) =
         \frac{\exp(U^m_{a,t})}
         {
            \sum_{j \in \mathcal{S}} \exp(U^j_{a,t})
         },\qquad \text{for } m \in \mathcal{S},
   \end{equation}
   where $\mathcal{S} = A_{a,t} \cap A_{b,t}$ is the set of mutual MoPs, which is
   the MoPs that both a buyer and a seller in the current transaction agree to use.
\end{definition}

For now, I simply assume that the deterministic part of the utility takes a
linear form
\begin{equation}
   U^m_{at}(\tilde{f}^m_{at}, i^m_t, X_t) = \beta_1 \tilde{f}^m_{at} + \beta_2 i^m_t
\end{equation}
Intuitively, we would expect $\beta_1$ to be positive since a more common MoP is
more likely to provide the agent with successful consumption, thus increasing
their future utility. On the other hand, we would expect $\beta_2$ to be
negative since using an MoP to purchase goods incurs a higher opportunity cost
compared to holding it as an asset and receiving interest. This is because using
the MoP for consumption means the agent cannot earn interest on the amount
spent, whereas holding the MoP as an asset allows them to earn interest on it.

\subsection{Portfolio Reallocation}

In the baseline model of \citet*{HandbookABM}, sellers (firms) observe their
inventories and price distribution of ones' neighbor and make adjustments on
price and production accordingly. In this model, however, the price mechanism is
pulled out to have a better focus on the transmission of new MoPs. Therefore,
the seller only has to reallocate its portfolio after receiving MoPs from
buyers. Imagine a shop owner depositing all his earnings in cash form to his
bank account.

During the reallocation, an agent considers three key components --- usage in
payment, future return, and cost in holding. Notice that there is actually a
tradeoff between using a monetary asset as an asset or not, hence you may notice
the symmetry between the decision process of using it as a means of payment or
an asset.

In the monetary search literature, a representative agent makes decision on the
portfolio to maximizes ones value function in a centralized market, where the
return of an asset is realized \citep*{LW05,LiLi19}. The value function of the
centralized market includes the value function of the decentralized market,
therefore the decision making of an agent's holding in the centralized market
indirectly affect the success rate of an exchange in the next subperiod.

In an ABM setting, however, we are unable, and unrealistic, to construct a
Bellman equation that captures the decision of MoP in the decentralized market
and the reallocation of the MoP as an asset simultaneously. Therefore I approach
this with another random utility model, with the same indicators an agent used
for MoP decision, but with a different set of parameter.

Similar to Eq. \ref{eq:MOP-utility}

\begin{equation}
   \label{eq:POR-utility}
   T^m_{at} = W^m_{at}(\tilde{f}^m_{at}, i^m_t, X_t) + \nu^m_{at} ,
\end{equation}
is the myopic utility of holding a MoP to the next period after reallocation.

\begin{center}
   (To be continued)
   (Trouble deciding what to do)
\end{center}

\subsection{Banks}

There is a home bank (HB) and a foreign bank (FB); each has its own deposit.
While ABM is capable of simulating a real-time gross settlement (RTGS) payment
system and endogenously capture the optimal process to cope with a liquidity
shock~\citep*{GS08-ABM-Payment}, for simplicity I set the proportion of illiquid
assets for a bank as an exogenous variable

\begin{definition}
   [Depositor's money allocation]
   \phantom{}\\
   Assume that the depositor puts in $v$ amount of MoP $m$ into a bank $b$,
   depending on its interoperability level $\xi_{m, b}\in [0,1]$, the bank adds
   $\xi_{m,b}v$ to its liability, and adds $\ell_b v$ to its capitals, and
   $(1-\ell_b) v$ to its reserves. $\ell_b$ is the capital adequacy ratio of the
   bank, and is set exogenously.
\end{definition}

I do not explicitly model the bank's asset portfolio, as well as its returns,
since this is not the focus of this paper. The reserves, however, is clearly
recorded. Moreover, the agents have transparent information about the leverage
rate (using dept-to-equity). Agents trigger a bank run panic through observing
this publicly announced information.

\subsection{Bank Run}

The bank run is triggered by an panic criteria and the followed up imitation behavior \citep*{Santos2021}.

\begin{definition}
   [Panic criteria]
   \phantom{}\\
   For an agent that has a D/E ratio tolerance ratio $\phi_a$, if the D/E ratio
   of a bank is higher than its tolerance ratio, $\mathrm{D/E}_b < \phi_a$, the
   agents withdraw all its deposits from the bank.
\end{definition}
Note that the tolerance ratio is heterogenous, so the bank run episode is not
going to happen like an avalanche. The key mechanism is the imitation behavior,
or herding behavior, that will spread the fear and causing the bank run to
realize.

\begin{definition}
   [Imitation Rule]
   \phantom{text} \\
   If more than $\zeta \in [0,1]$ ratio of agents in its network withdraws from
   bank $b$ in past $T_{br}$ period, then the agent also withdraws, no matter
   whether the D/E ratio exceeds it tolerance ratio or not.

\end{definition}


\subsection{Buyer-Seller Toggle}
To motivate the adoption of a means of payment, it is necessary to let the
receiver of a MoP, which is the seller, to have the opportunity of purchasing in
the same economy. In this model, I simply let the buyer become a seller and a
seller become a buyer periodically.

All information about the MoP is passed down as state variables despite the
agent is acting as a different role in the upcoming period. In other words, the
MoP that a buyer is willing to pay is the MoP that one is willing to accept,
unless while proceeding to the next period the agent observes enough occurrence
of that MoP such that it starts to accept it in the next period.

Seller reallocate its portfolio before turning into a buyer, this is a
reasonable timing since the reallocation can affect the success rate of a trade
in the next period.